---
title: "Assignment"
author: "nabiha faisal"
date: "1/19/2022"
output: word_document
---

```{r}
data(rock)  
head(rock) 
dim(rock) 
#there are 48row and 4 col in this data

print(summary(rock))



```                   
#2.plots
-----------------------
```{r}

library(ggplot2)
attach(rock)


hist(shape,breaks= 15,  col = 'red',
     xlab= 'shape', 
     main = 'shape of rock')
#graph shows the max observation lies between 0.1 and 0.2 and it is roughly bell shaped
boxplot(area ~ peri, main="Fig.-1: Boxplot of shape of four type of rock", col= rainbow(3))
#graph shows as area in creases the perimeter in pixels also increase
plot(shape,perm, col = "Blue")

scatter.smooth(x=area,y=shape,main="rock")

barplot(shape, main="shape of rocks",
   xlab="shape")
#the biggest rock shape is greater than 0.4
```
#3.correlation
------------------------
```{r}

cor(rock)

#area is closely related to peri(perimeter in pixels of the rock)
#shape is closely related to perm of the rock


# -----------------------------------------------------------------------------
library(corrplot)

cor.mat.rock = cor(rock)
corrplot(cor.mat.rock)

```

#3.confidence interval
-------------------------------
```{r}


library(Rmisc)
attach(rock)

CI(shape, ci = 0.95) # Calculates the confidence interval of a vector of data.

#mean lies between the confidence interval we accept the null hypothesis

plot(density(shape))
shapiro.test(shape)
# p value <0.05 so the data is not normall distributed


```

# 4.Hypothesis testing
# -------------------
```{r}

library(stats)

# One sample t-test
# -------------------
t.test(rock$shape, mu = 0.21) # to test: Is the mean value of mpg differ from 20 or not?
#alternative hypoyhesis  not rejected
t.test(rock$shape, mu =0.21 , alternative = 'greater') # if you want to test on sided alternative.
library(gginference)
ggttest(t.test(rock$shape, mu = 0.21))
# 
# ----------------------------------------------





```
#5.Chi-square test
# ---------------
```{r}

attach(rock)


chisq.test(perm,shape)
#there is no association between the shape and permiablity of rock
chisq.test(area,shape)
#there is slight association between the area and shape
# --------------------
```

#6.Analysis of Variance
# --------------------
```{r}
 
attach(rock)

# ONE WAY ANOVA 

boxplot(shape ~area, col= rainbow(5))


model1 <- aov(shape ~area)
summary(model1)

#F value is greater than P value so we will reject the null hypothesisand thus the shape per area is not equal.
#null hypothesis=shape per area is equal
#alternative hypothesis= shape per area not equal.

``````

# 7.Linear and Multiple Regression Models:
# --------------------------------------
```{r}
# Linear Regression line formula:
# -------------------------------
attach(rock)

fit.LR <- lm(area ~ shape, data = rock)
summary(fit.LR)
#equation:
#area=8465+(-5855)shape
#comments:
#intercept is significant for this segregation
#regulation model in not good overall 
#corroletion between area and shape is 18%
#p value shows that with decrease in shape will result in increase in area

scatter.smooth(x=area,y=shape,main="rock")
require(ggplot2)
ggplot(rock,aes(y=shape,x=area))+geom_point()+geom_smooth(method = "lm")
#plot shows us the linearity and independence of observation 



##t test for intercept

# Multiple Regression line formula:
# -------------------------------


fit.MR <- lm(area ~ shape + peri + perm, data = rock)
summary(fit.MR)
#equation:
#area=-407.06+2992shape+2.19peri+2.54perm
#intercept is not significant for this segregation
#change in shape is not significant with change in area  whereas change in  perimeter and permiability are highly significant with change in area
#corroletion between area and these three variables is 88%

  

#t test for intercept 
#________________________

#t_{b_{0}}=\frac{b_{0}-\beta_{0}}{s_{b_{0}}}

#t test for slope
#__________________

#t_{b_{1}}=\frac{b_{1}-\beta_{1}}{s_{b_{1}}}  
 
  

# Is the overall regression model suitable?
# ---------------------------------------
anova(fit.LR)  # Test difference in slopes (joint F-test)
#f value is grater than p value so we will reject null hypothesis
# The F-statistic value tells result is not good overall

```
